Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-06-06 latex/afm-cs-main.tex
Update the metrics figs to include a custom colorbar legend.

\begin{figure*}[h!]
  \begin{subfigure}{0.33\textwidth}
    \includesvg[width=\textwidth]{figures/cs_rast_time_vs_ssim.svg}
    \caption{}
    \label{fig:time_ssim}
  \end{subfigure}
  \begin{subfigure}{0.33\textwidth}
    \includesvg[width=1\textwidth]{figures/cs_rast_time_vs_psnr.svg}
    \caption{}
    \label{fig:time_psnr}
  \end{subfigure}
  \begin{subfigure}{0.33\textwidth}
    \includesvg[width=\textwidth]{figures/cs_rast_damage.svg}
    \caption{}
    \label{fig:time_damage}
  \end{subfigure}
\caption{Metrics for raster scan and $\mu$-path scans at 10\% and 15\% sampling. (a) SSIM as a function of total acquisition time. (b) PSNR  as a function of total acquisition time. (c) RDI as a function of total acquisition time.}

>>>>

\begin{figure*}[h!]
  \centering
  \begin{subfigure}{1\textwidth}
    \centering
    \includesvg[width=0.8\textwidth]{figures/cs_rast_time_vs_ssim.svg}
    \caption{}
    \label{fig:time_ssim}
  \end{subfigure}
  \begin{subfigure}{1\textwidth}
    \centering
    \includesvg[width=0.8\textwidth]{figures/cs_rast_time_vs_psnr.svg}
    \caption{}
    \label{fig:time_psnr}
  \end{subfigure}
  \begin{subfigure}{1\textwidth}
    \centering
    \includesvg[width=0.8\textwidth]{figures/cs_rast_damage.svg}
    \caption{}
    \label{fig:time_damage}
  \end{subfigure}
\caption{Metrics for raster scan and $\mu$-path scans at 10\% and 15\% sampling. (a) SSIM as a function of total acquisition time. (b) PSNR  as a function of total acquisition time. (c) RDI as a function of total acquisition time. The scan rate is indicated by color while the scan style is indicated by marker style.}
